---
title: "HW 10"
author: "Jillian Egland"
date: "2023-04-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Homework 10 
team: Jillian Egland 
https://github.com/jcegland/DS202-Spring2023 



## Read in data 
```{r, warning=FALSE} 
library(tidyverse)
accident = read.csv("https://raw.githubusercontent.com/yumouqiu/DS202-Spring2023/main/Practice/data/fars2016/accident.csv")
person = read.csv("https://raw.githubusercontent.com/yumouqiu/DS202-Spring2023/main/Practice/data/fars2016/person.csv")
vehicle = read.csv("https://raw.githubusercontent.com/yumouqiu/DS202-Spring2023/main/Practice/data/fars2016/vehicle.csv")

head(accident)
head(person)
head(vehicle)

```


# plotting lat and long on map 

```{r} 

ggplot(accident, aes(x=LONGITUD, y=LATITUDE)) + geom_point() 

accident_filter = dplyr::filter(accident, LONGITUD<500)
ggplot(accident_filter, aes(x=LONGITUD, y=LATITUDE)) + geom_point() 




``` 


# Days of the week 
are there some days of the week where more accidents happen than on others (use variable DAY_WEEK)? 
  Assuming 1 is Sunday, it looks like accidents are increased on the weekends, and lower towards the middle of the week. 

```{r} 
ggplot(accident_filter, aes(x=DAY_WEEK) ) + geom_bar() 




``` 


# Time of the day 
what time of the day do accidents happen (use variable HOUR)?
  there is a small increase in accidents in the morning as people drive to work and a larger hump from noon to midnight with a peak at 5 in the afternoon as people drive home from work. 


```{r} 
accident_filter = dplyr::filter(accident_filter, HOUR<25)
ggplot(accident_filter, aes(x=HOUR) ) + geom_bar()



``` 



# Drunk Driving 
what is the number of accidents with at least one drunk driver (use variable DRUNK_DR)?
  8,720 accidents with at least one drunk driver  


```{r} 

ggplot(accident, aes(x=DRUNK_DR) ) + geom_bar() 

nrow(dplyr::filter(accident, DRUNK_DR>0))



``` 




# Connecting Person and Accident  
Connect to the person table. Identify drivers (PER_TYP == 1, see fars manual ) and subset on them.

Join accident and driver table (work out which variable(s) to use)

Tally the number of accidents by day of the week (DAY_WEEK), hour of the day (HOUR) and gender (SEX). Visualize the results!


```{r} 
drivers = dplyr::filter(person, PER_TYP == 1)
combo_data = left_join(accident, drivers, by="ST_CASE")


ggplot(combo_data, aes(x=DAY_WEEK) ) + geom_bar() +
geom_text(stat='count', aes(label=..count..), vjust=-1)

combo_data_filter = dplyr::filter(combo_data, HOUR.x<25)
ggplot(combo_data_filter, aes(x=HOUR.x) ) + geom_bar()+
geom_text(stat='count', aes(label=..count..), vjust=-1)

combo_data_filter2 = dplyr::filter(combo_data, SEX<3)
ggplot(combo_data_filter2, aes(x=SEX)) + geom_bar()+
geom_text(stat='count', aes(label=..count..), vjust=-1)



``` 













