---
title: "HW 5"
author: "Jillian"
date: "2023-03-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Assignment 
Group members: Jillian Egland 
repo link: 

Workflow paragraph: 





# importing data 

```{r}
library(ggplot2) 
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco) 
str(choco)




```







# Question Set 1

1. What is the overall number of chocolate bars rated?
2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports. 

```{r} 






```




# Question Set 2 

(provide at least one graphic as basis for the answers )
1. How are ratings distributed? Draw a histogram of ratings and describe it. Don’t forget to mention outliers, if there are any.
2. Do ratings depend on the cocoa percentage of a chocolate bar?
3. How do ratings compare across different company locations? Focus on the three locations with the most ratings: 

```{r} 
top3 <- dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))






```



# My Question 

1. Question 
2. Graphs 
3. Conclusion 

```{r}




``` 









